Summary of models

### 2022-10-05 Rmd/Models.Rmd
visitation rate (Apis and no Apis)

Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

@@

visitation rate is calculated like frequency/ flower abundance

@@

@@

@@

@@

>>>>

Pollinator_Plant<- read.csv("../Data/Pollinator_Plant_Apis_separada.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

@@

Visitation rate of all pollinators (hymenoptera, diptera and coleoptera) is calculated like frequency/ flower abundance

@@

## Visitation rate of pollinators without Apis mellifera

visitation rate (frequency/ flower abundance) is calculated to all pollinators no apis mellifera.

mod_fruitproportion_polli_no_api<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_fruitproportion_polli_no_api<-mod_fruitproportion_polli_no_api %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruitproportion_polli_no_api<-filter(mod_fruitproportion_polli_no_api, !term == "sd__(Intercept)")

mod_fruitproportion_polli_no_api %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_fruitproportion_polli_no_api$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_fruitproportion_polli_no_api_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion_polli_no_api_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_fruitproportion_polli_no_api.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "No_Apis_visit_rate"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1= mod_fruitproportion_polli_no_api.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2= mod_fruitproportion_polli_no_api.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_fruitproportion_polli_no_api.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4= mod_fruitproportion_polli_no_api.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5= mod_fruitproportion_polli_no_api.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6= mod_fruitproportion_polli_no_api.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7= mod_fruitproportion_polli_no_api.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8= mod_fruitproportion_polli_no_api.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9= mod_fruitproportion_polli_no_api.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10= mod_fruitproportion_polli_no_api.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11=mod_fruitproportion_polli_no_api.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12= mod_fruitproportion_polli_no_api.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

## Apis mellifera visitation rate

Only data of Apis mellifera

# visistation rate A.mellifera
mod_fruitproportion__apis<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_fruitproportion__apis<-mod_fruitproportion__apis %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruitproportion__apis<-filter(mod_fruitproportion__apis, !term == "sd__(Intercept)")

mod_fruitproportion__apis %>% 
kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_fruitproportion__apis$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_fruitproportion__apis_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion__apis_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_fruitproportion__apis.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms ="Apis_visit_rate")))   %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1= mod_fruitproportion__apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2= mod_fruitproportion__apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_fruitproportion__apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4= mod_fruitproportion__apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5= mod_fruitproportion__apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6= mod_fruitproportion__apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7= mod_fruitproportion__apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8= mod_fruitproportion__apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9= mod_fruitproportion__apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10= mod_fruitproportion__apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11=mod_fruitproportion__apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12= mod_fruitproportion__apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

## Hymenoptera visitation rate without A.mellifera

mod_fruitproportion_hyme_no_apis<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_fruitproportion_hyme_no_apis<-mod_fruitproportion_hyme_no_apis %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruitproportion_hyme_no_apis<-filter(mod_fruitproportion_hyme_no_apis, !term == "sd__(Intercept)")

mod_fruitproportion_hyme_no_apis %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_fruitproportion_hyme_no_apis$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_fruitproportion_hyme_no_apis_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion_hyme_no_apis_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_fruitproportion_hyme_no_apis.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit_sin_apis"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1 = mod_fruitproportion_hyme_no_apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2 = mod_fruitproportion_hyme_no_apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3 = mod_fruitproportion_hyme_no_apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4 = mod_fruitproportion_hyme_no_apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5 = mod_fruitproportion_hyme_no_apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6 = mod_fruitproportion_hyme_no_apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7 = mod_fruitproportion_hyme_no_apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8 = mod_fruitproportion_hyme_no_apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9 = mod_fruitproportion_hyme_no_apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10 = mod_fruitproportion_hyme_no_apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11 = mod_fruitproportion_hyme_no_apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12 = mod_fruitproportion_hyme_no_apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

## Visitation rate
Visitation rate of all pollinators (hymenoptera, diptera and coleoptera)

@@

## Visitation rate of pollinators without Apis mellifera

mod_seed_Vr_no_apis<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~No_Apis_visit_rate+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_seed_Vr_no_apis<-mod_seed_Vr_no_apis %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed_Vr_no_apis<-filter(mod_seed_Vr_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")

mod_seed_Vr_no_apis %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_Vr_no_apis$p.value < 0.05, T, F)) %>% kable_styling(position="center", latex_option="hold_position")

mod_seed_Vr_no_apis_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~No_Apis_visit_rate+(1|Site_ID),data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_seed_Vr_no_apis_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")

# model plot 
mod_seed_Vr_no_apis_trial.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~No_Apis_visit_rate+(1|Site_ID),data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "No_Apis_visit_rate"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1 = mod_seed_Vr_no_apis_trial.2 $ plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x = No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate",y ="seed_number",subtitle = "A.fistulosus") + theme_classic()+theme(text = element_text(size=rel(3)))

p2 = mod_seed_Vr_no_apis_trial.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "C.crispus")+ theme_classic()+theme(text = element_text(size=rel(3)))

p3 = mod_seed_Vr_no_apis_trial.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "C.ladanifer")+ theme_classic()+theme(text = element_text(size=rel(3)))

p4 = mod_seed_Vr_no_apis_trial.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate", y ="seed_number",subtitle = "C.libanotis")+ theme_classic()+theme(text = element_text(size=rel(3)))

p5 = mod_seed_Vr_no_apis_trial.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate", y = "seed_number", subtitle = "C.monspeliensis")+theme_classic()+theme(text = element_text(size=rel(3)))

p6 = mod_seed_Vr_no_apis_trial.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate", y = "seed_number",subtitle = "C.salviifolius")+ theme_classic()+theme(text = element_text(size=rel(3)))

p7 = mod_seed_Vr_no_apis_trial.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate", y = "seed_number",subtitle = "H.calycinum") + theme_classic()+theme(text = element_text(size=rel(3)))

p8 = mod_seed_Vr_no_apis_trial.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate", y = "seed_number",subtitle = "H.halimifolium")+ theme_classic()+theme(text = element_text(size=rel(3)))

p9 = mod_seed_Vr_no_apis_trial.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10 = mod_seed_Vr_no_apis_trial.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11 = mod_seed_Vr_no_apis_trial.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12 = mod_seed_Vr_no_apis_trial.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

## Visitation rate of Apis mellifera

mod_seed_Vr_apis<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Apis_visit_rate+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

mod_seed_Vr_apis<-mod_seed_Vr_apis %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed_Vr_apis<-filter(mod_seed_Vr_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")

mod_seed_Vr_apis %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_Vr_apis$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

mod_seed_Vr_apis_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Apis_visit_rate+(1|Site_ID),data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_seed_Vr_apis_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

# model plot 
mod_seed_Vr_apis_trial.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Apis_visit_rate+(1|Site_ID),data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Apis_visit_rate"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1 = mod_seed_Vr_apis_trial.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2 = mod_seed_Vr_apis_trial.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+  labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3 = mod_seed_Vr_apis_trial.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4 = mod_seed_Vr_apis_trial.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5 = mod_seed_Vr_apis_trial.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6 = mod_seed_Vr_apis_trial.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7 = mod_seed_Vr_apis_trial.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8 = mod_seed_Vr_apis_trial.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9 = mod_seed_Vr_apis_trial.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10 = mod_seed_Vr_apis_trial.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
